Structuring College Access

### 2025-02-26 index.qmd
revisions to the way figures and presentation created

  # 'metro' is already underscored (e.g. "los_angeles").
  # We'll use it directly for file paths, but if you want
  # to be extra safe, you can do:
  # metro_underscored <- str_replace_all(metro, " ", "_")
  # ... (assuming it has no spaces).

  fig_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_note.txt"))

@@

  # Convert "los_angeles" -> "Los Angeles" for display in slides
  heading_text <- gsub("_", " ", m, fixed = TRUE)
  heading_text <- tools::toTitleCase(heading_text)

  # Print a top-level heading for the metro area in user-friendly form
  writeLines(str_c("## ", heading_text, " area"))

@@

      # Use 'm' for the file path to the map (underscored version).
      # If you had a special case for "los_angeles", you could handle that here.
      rq1_map <- str_c('./results/maps/rq1_map_', m, '.html')

      # But let's illustrate one special example for "los_angeles":
      if (m == "los_angeles") {
        rq1_map <- 'https://rq1-map-los-angeles.netlify.app'
      }

@@

              # e.g. "race_col_plot_448375_546954"
              # => "rq2_los_angeles_race_col_plot_448375_546954.png"
              graph_type_col <- str_c(g, "_", rc, "_plot_", order_id)
              insert_figure(rq = rq, metro = m, graph_type = graph_type_col)
            }

>>>>

  # We'll use 'metro' directly since it's already underscored (e.g. "los_angeles").
  fig_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_note.txt"))

@@

  # Convert underscores -> spaces, then title case
  # But add special checks for "dc_maryland_virginia" and "bay_area"
  if (m == "dc_maryland_virginia") {
    heading_text <- "D.C., Maryland, and Virginia"
  } else if (m == "bay_area") {
    heading_text <- "Bay Area"
  } else {
    # Normal logic
    heading_text <- gsub("_", " ", m, fixed = TRUE)
    heading_text <- tools::toTitleCase(heading_text)
    heading_text <- str_c(heading_text, " area")
  }

  # Print a top-level heading for the metro area
  writeLines(str_c("## ", heading_text))

@@

      rq1_map <- str_c('./results/maps/rq1_map_', m, '.html')

      # Example special case for "los_angeles"
      if (m == "los_angeles") {
        rq1_map <- 'https://rq1-map-los-angeles.netlify.app'
      }

@@

              graph_type_col <- str_c(g, "_", rc, "_plot_", order_id)
              insert_figure(rq = rq, metro = m, graph_type = graph_type_col)
            }
